ms2

### 2017-05-04 ms2/ms2.Rmd
new plots ,etc.

```{r fnz-mean, cache=FALSE}
ggplot(all_ineq, aes(x=mean, y=fnz, color=region, label=state_abbreviation)) +
geom_point() +
geom_text(nudge_x=0.04) +
xlab('claims per beneficiary') +
ylab('fraction of beneficiaries w/ >= 1 claim') +
theme_minimal()
```

@@

```{r nzgini-mean, cache=FALSE}
ggplot(all_ineq, aes(x=mean, y=nzgini, color=region, label=state_abbreviation)) +
geom_point() +
geom_text(nudge_x=0.04) +
xlab('claims per beneficiary') +
ylab('Gini coefficient among benes. w/ >= 1 claim') +
theme_minimal()
```

@@

abg %<>% right_join(good_combos, by=c('bug', 'drug_group')) %>%
  rename(bug_long=bug) %>% left_join(bug_names, by='bug_long') %>% select(-bug_long)

@@

summarize_abg = function(df, place_name) {
    group_by_(df, 'bug', 'drug_group', place_name) %>%
    summarize(mean_percent_nonsusceptible=weighted.mean(percent_nonsusceptible, sqrt(n_isolates)),
              n_place_antibiograms=n()) %>%
    mutate(place_weight=sqrt(n_place_antibiograms))
}

@@

```{r spearman_models, cache=FALSE}
results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj, n_data) %>%
  kable
```

@@

```{r hrr_spearman_models, cache=FALSE}
hrr_results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj, n_data) %>%
  kable
```

@@

```{r univariate_models, cache=FALSE}
results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r hrr_univariate_models, cache=FALSE}
hrr_results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.adj) %>%
  kable
```

@@

```{r multivariate_models, cache=FALSE}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.value < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

And what about looking at multivariate only for ones that passed the threshold for univariate? Doesn't seem like it works for any of them!

@@

When using the HRRs, some of the values remained significant even after correction. I show all those values that passed the unadjusted threshold (like above):

@@

hrr_results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  #right_join(sig_bug_drug, by=c('bug', 'drug_group')) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r nzgini_cpb_drug}
cbbPalette <- c("#000000", "#D55E00", "#CC79A7", "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")
state_ineq %>%
  ggplot(aes(x=nzgini, y=mean, color=drug_group)) +
  geom_point() +
  xlab('nonzero Gini') + ylab('claims per beneficiary') +
  theme_minimal() +
  scale_color_manual(values=cbbPalette)
```

@@

```{r ecoli_bactrim}
ecoli_bactrim_dat = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='E. coli', drug_group=='tmp_smx') %>%
  filter(!is.na(mean_percent_nonsusceptible))

@@

>>>>

```{r fnz_mean, cache=FALSE}
ggplot(all_ineq, aes(x=mean, y=fnz, color=region, label=state_abbreviation)) +
geom_point() +
geom_text(nudge_x=0.04) +
xlab('claims per beneficiary') +
ylab('fraction of beneficiaries w/ >= 1 claim') +
theme_minimal()
```

@@

```{r nzgini_mean, cache=FALSE}
ggplot(all_ineq, aes(x=mean, y=nzgini, color=region, label=state_abbreviation)) +
geom_point() +
geom_text(nudge_x=0.04) +
xlab('claims per beneficiary') +
ylab('Gini coefficient among benes. w/ >= 1 claim') +
theme_minimal()
```

@@

abg %<>% right_join(good_combos, by=c('bug', 'drug_group')) %>%
  rename(bug_long=bug) %>% left_join(bug_names, by='bug_long') %>% select(-bug_long) %>%
  filter(!is.na(percent_nonsusceptible), !is.na(n_isolates))

@@

summarize_abg = function(df, place_name) {
    group_by_(df, 'bug', 'drug_group', place_name) %>%
    summarize(mean_percent_nonsusceptible=weighted.mean(percent_nonsusceptible, sqrt(n_isolates)),
              n_place_antibiograms=n()) %>%
    #filter(!is.na(mean_percent_nonsusceptible)) %>%
    mutate(place_weight=sqrt(n_place_antibiograms))
}

@@

```{r spearman_models, cache=FALSE}
results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r hrr_spearman_models, cache=FALSE}
hrr_results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r univariate_models, cache=FALSE}
results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r hrr_univariate_models, cache=FALSE}
hrr_results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r multivariate_models, cache=FALSE}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

And what about looking at multivariate only for ones that passed the threshold for univariate?

@@

Using HRRs, adjusting $p$ with all possibilities:

```{r cache=FALSE}
hrr_results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

And then doing multiple hypothesis correction only for those that made it through the first model:

@@

hrr_results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  right_join(sig_bug_drug, by=c('bug', 'drug_group')) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r nzgini_cpb_drug}
cbbPalette <- c("#000000", "#D55E00", "#CC79A7", "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")
state_ineq %>%
  ggplot(aes(x=mean, y=nzgini, color=drug_group)) +
  geom_point() +
  ylab('Gini coefficient among users') + xlab('claims per beneficiary') +
  theme_minimal() +
  scale_color_manual(values=cbbPalette)
```

@@

```{r ecoli_bactrim}
ecoli_bactrim_dat = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='E. coli', drug_group=='tmp_smx') #%>%
  #filter(!is.na(mean_percent_nonsusceptible))

@@

## MSSA and clindamycin

```{r mssa_clinda}
dat = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='MSSA', drug_group=='clindamycin') #%>%
  #filter(!is.na(mean_percent_nonsusceptible))

dat %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  #scale_x_continuous(limits=c(0.08, 0.2), breaks=c(0.08, 0.1, 0.15, 0.2)) +
  #ylim(10, 45) +
  xlab('clindamycin claims per beneficiary') + ylab('mean percent nonsusceptible MSSA isolates') +
  theme_minimal()

dat %>%
  { mutate(., excess_resistance=residuals(lm(mean_percent_nonsusceptible ~ mean, data=.))) } %>%
  ggplot(aes(x=nzgini, y=excess_resistance)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  #scale_x_continuous(limits=c(0.25, 0.375)) +
  #scale_y_continuous(limits=c(-12, 20), breaks=c(-12, 0, 10, 20)) +
  xlab('Gini coefficient') +
  ylab('"Excess" MSSA resistance') +
  theme_minimal()
```
